Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-17 paper/paper.tex
quick pass

\subsection{\Fix{JBoss JMX Console Beanshell Deployer WAR Upload and Deployment Exploit}}
\label{sec:jboss}

@@

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. \tname\ takes on input malicious and benign traffic and a
set of rules from public rulesets and produces on output a list of
plausible rules to isolate the malicious
traffic. Figure~\ref{fig:overview} shows the workflow of \tname{} as a
pipeline of three components, which appear numbered in the figure.
The inputs of the technique appear at the bottom of the figure whereas
the output appears at the right.

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, provided on
input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options in correspondence with the input messages
(see Section~\ref{sec:rules-and-packets}). It is worth noting that the
rule produced in this step can include more options than the golden
rule (see Section~\ref{sec:suri-metas-coverage}). Consequently, the
use of that rule could lead, in principle, to false negatives as not
all manifestations of the same attack are identical. Second, \tname{}
generates plausible rules similar to the one produced in the previous
step. It is worth noting that any subset of the original set of
options captures the malicious traffic. As the generation procedure
discards options from the initial rule, it satisfies the invariant of
capturing malicious traffic by construction. However, the goal of
\tname\ is to produce rules that capture \emph{only} malicious
traffic. To achieve that goal, \tname{} uses benign traffic from
public databases to check that the \nids\ instantiated with a given
rule does not capture benign traffic. The minimization step uses a
population-based gradient descent-like search to find all plausible
rules, which are derived from the rule obtained in the previous
step. Third, uses several heuristic functions derived from a dataset
of rules to rank the rules generated in the previous step.

@@

For that, \tname{} parses the message looking for options associated
with the data. As described in Section~\ref{sec:rules-and-packets},
there is a correspondence between packet fields and rule
options. \tname{} leverages that mapping to infer options. The
examples of sections~\ref{sec:dos} and~\ref{sec:active-recon} show
cases where \tname{} infers options with this mapping. Unfortunately,
inferring options at the field granularity level is insufficient to
capture \CodeIn{content} options as the described on
Section~\ref{sec:content-example}. These options refer to parts of the
payload of the message and cannot be extracted directly from the
fields. Handling this case is critically important as 93\% of
the rules contain \CodeIn{content} options.

@@

\Gui{
O procedimento que já tínhamos representa a etapa de treinamento. Toda aquela parte que foi explicada na apresentação para os outros professores e descrito no paper. Descreverei novamente pra confirmar, e também foi adicionado uma pequena etapa.

TREINAMENTO

->Syrius recebe como input um pcap contendo o ataque (no caso de ataques com content, usamos ataques do Nikto), um pcap benígno (usamos o bigflows.pcap) e um pcap contendo as variações de ataque (isso pode ser otimizado unificando com o pcap de ataque, mas por agora está assim)
->É gerado a regra máxima através do tokenizer e engenharia reversa.
->Syrius remove UM content de uma regra da lista de regras atuais (inicialmente apenas a regra máxima) e checa se a regra criada já existe na lista. Se não, a regra é adicionada à lista de regras-não-testadas. Syrius faz isso duas vezes por regra, para todas as regras da lista.
->A lista de regras-não-testadas é inicializada no suricata e então o rodamos com o pcap benígno de treinamento (75porcento do total). Verificando no arquivo de log do suricata, caso a regra alerte, ela é removida da lista. As regras restantes vão para a lista de regras atuais.
->Quando não houver alterações, retornamos a lista com todas as regras que deram certo.
->Opcionalmente, ainda rodamos no final uma variação de ataque (no momento apenas um pacote devido ao número limitado que temos do ataque). Ao contrário do método com pacotes benígnos, se a regra NÃO alertar, ela é removida.
->Calculamos o fitness de cada regra e ordenamos de acordo com o fitness resultante. Esta lista ordenada é o fim do treinamento.

TESTE

->Inicializamos a lista de regras ordenadas no suricata e rodamos o pcap benígno de teste (25porcento restantes) para cálculo do precision. O cálculo ficou basicamente, por regra: [100 - (numero-de-alertas/total-de-pacotes)]

->Inicializamos a lista de regras ordenadas no suricata e rodamos o pcap com variações de ataque (caso a etapa opcional ocorrer, não usamos aquele pacote especifico) para cálculo do recall. O cálculo ficou basicamente, por regra: [(100/total-de-pacotes) * n-alertas].

->Por final calculamos o F1 Score por regra: [2*((precision*recall)/(precision+recall))]

->O teste retorna um csv contendo a lista de regras ordenadas com seus respectivos precision, recall e f1 score.
}

>>>>

\subsection{\Fix{JBoss JMX Console Beanshell Deployer WAR Upload and Deployment Exploit}}
\label{sec:jboss}
\label{sec:content-example}

@@

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. \tname\ takes on input malicious and benign traffic and a
set of rules from public rulesets and produces on output a list of
plausible rules to isolate the malicious from the benign
traffic. Figure~\ref{fig:overview} shows the workflow of \tname{} as a
pipeline of three components, which appear numbered in the figure.
The inputs of the technique appear at the bottom of the figure whereas
the output appears at the right.

\tname\ works as follows. First, it produces a potentially
overspecified rule that captures the malicious traffic, provided on
input in the form of pcap files~\cite{pcap}. In this step,
\tname\ detects rule options directly from the input messages (see
Section~\ref{sec:rules-and-packets}). As only malicious traffic is
considered in this step, the rule produced is likely overspecified,
\ie{}, it includes more options than the golden rule (see
Section~\ref{sec:suri-metas-coverage}). Consequently, the use of that
rule could lead to false negatives as not all manifestations of the
same attack are identical. Second, \tname{} generates plausible rules
that are similar to the seed rule produced in the previous step. It is
worth noting that any subset of the original set of options captures
the malicious traffic. \tname{} leverages that observation to search
for rules containing a proper subset of rules defined in the original
seed option. As the generation procedure discards options from the
initial rule, the rules \tname{} creates satisfies the property of
capturing malicious traffic. However, the goal of \tname\ is to
produce rules that capture \emph{only} malicious traffic. To achieve
that goal, \tname{} uses benign traffic to reduce the likelihood the
\nids\ will report false positives on the synthesized rule. The
minimization step uses a population-based gradient descent-like search
to find all plausible rules derived from the seed rule, obtained in
the previous step. Third, \tname{} uses several heuristic functions
derived from a dataset of rules to rank the rules generated in the
previous step.

@@

For that, \tname{} parses the message looking for options associated
with the data. As described in Section~\ref{sec:rules-and-packets},
there is a correspondence between packet fields and rule
options. \tname{} leverages that mapping to infer options. The
examples of sections~\ref{sec:dos} and~\ref{sec:active-recon} show
cases where \tname{} infers options with this mapping. Unfortunately,
inferring options at the field granularity level is insufficient to
capture content options as those described on
Section~\ref{sec:content-example}. These options refer to parts of the
payload of the message and cannot be extracted directly from the
fields. Handling this case is critically important as 93\% of the
rules contain \CodeIn{content} options.

@@

%% \Gui{
%% O procedimento que já tínhamos representa a etapa de treinamento. Toda aquela parte que foi explicada na apresentação para os outros professores e descrito no paper. Descreverei novamente pra confirmar, e também foi adicionado uma pequena etapa.

%% TREINAMENTO

%% ->Syrius recebe como input um pcap contendo o ataque (no caso de ataques com content, usamos ataques do Nikto), um pcap benígno (usamos o bigflows.pcap) e um pcap contendo as variações de ataque (isso pode ser otimizado unificando com o pcap de ataque, mas por agora está assim)
%% ->É gerado a regra máxima através do tokenizer e engenharia reversa.
%% ->Syrius remove UM content de uma regra da lista de regras atuais (inicialmente apenas a regra máxima) e checa se a regra criada já existe na lista. Se não, a regra é adicionada à lista de regras-não-testadas. Syrius faz isso duas vezes por regra, para todas as regras da lista.
%% ->A lista de regras-não-testadas é inicializada no suricata e então o rodamos com o pcap benígno de treinamento (75porcento do total). Verificando no arquivo de log do suricata, caso a regra alerte, ela é removida da lista. As regras restantes vão para a lista de regras atuais.
%% ->Quando não houver alterações, retornamos a lista com todas as regras que deram certo.
%% ->Opcionalmente, ainda rodamos no final uma variação de ataque (no momento apenas um pacote devido ao número limitado que temos do ataque). Ao contrário do método com pacotes benígnos, se a regra NÃO alertar, ela é removida.
%% ->Calculamos o fitness de cada regra e ordenamos de acordo com o fitness resultante. Esta lista ordenada é o fim do treinamento.

%% TESTE

%% ->Inicializamos a lista de regras ordenadas no suricata e rodamos o pcap benígno de teste (25porcento restantes) para cálculo do precision. O cálculo ficou basicamente, por regra: [100 - (numero-de-alertas/total-de-pacotes)]

%% ->Inicializamos a lista de regras ordenadas no suricata e rodamos o pcap com variações de ataque (caso a etapa opcional ocorrer, não usamos aquele pacote especifico) para cálculo do recall. O cálculo ficou basicamente, por regra: [(100/total-de-pacotes) * n-alertas].

%% ->Por final calculamos o F1 Score por regra: [2*((precision*recall)/(precision+recall))]

%% ->O teste retorna um csv contendo a lista de regras ordenadas com seus respectivos precision, recall e f1 score.
%% }
